### 2024-04-19 docs/SOSP 2024/results.tex
Shrink figures in results

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_4060_kernel_time_total_time.png}
  \caption{\Treebeard{} vs RAPIDS and Tahoe kernel time and total time speedup (geomean over real-world 
  benchmarks) across batch sizes on NVIDIA RTX 4060}
  \label{Fig:TBvsRAPIDSTahoe_4060_Speedup}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_T400_kernel_time.png}
  \caption{\Treebeard{} vs RAPIDS and Tahoe kernel time and total time speedup (geomean over real-world 
  benchmarks) across batch sizes on NVIDIA T400.}
  \label{Fig:TBvsRAPIDSTahoe_T400_Speedup}
\end{figure}

\begin{figure*}[ht]
  \centering
  \begin{subfigure}[b]{.45\textwidth}
    \subcaptionbox*{}{\includegraphics[width=\textwidth]{figures/speedup_bar_graph_1024.png}}
    \caption{Batch size 1024}
  \end{subfigure}
  \begin{subfigure}[b]{.45\textwidth}
    \subcaptionbox*{}{\includegraphics[width=\textwidth]{figures/speedup_bar_graph_8192.png}}
    \caption{Batch size 8192}
  \end{subfigure}
  \hfill
  \caption{\label{Fig:KernelTimeIndividualBenchmarks4060}Kernel time speedup of \Treebeard{} vs RAPIDS on NVIDIA RTX 4060. Numbers on the bars are 
  inference times per sample in $\mu$s for RAPIDS and Tahoe.}
\end{figure*}

Figure~\ref{Fig:KernelTimeIndividualBenchmarks4060} shows per benchmark results at two different batch sizes. 
\Treebeard{} is able to find better schedules than both RAPIDS and Tahoe on each of the benchmarks. It consistently
outperforms both systems, achieving a speedup of upto $12\times$ an average speedup of over $2\times$.
For about half the benchmarks, the speedup is $2\times$ or more over both baselines at batch size 8192.

@@

\begin{figure}[htb]
  \begin{minipage}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b512_depth8.png}
    %\caption{Batch size 512}
  \end{minipage}
  \begin{minipage}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b4096_depth6.png}
    %\caption{Batch size 4096}
  \end{minipage}
  \caption{\label{fig:randomModels4060}\Treebeard{} vs RAPIDS Kernel Time Speedup for random models
  of max depth 8 at batch size 512 and max depth 6 at batch size 4096.}
\end{figure}

@@

% \subsection{Comparison with RAPIDS, Tahoe and XGBoost}
% \begin{itemize}
%   \item Measured both the kernel time and total time (time including transferring data to the 
%   GPU and results back) for RAPIDS and \Treebeard{}.
%   \item Tahoe only allows us to measure the kernel time since it is written as an executable 
%   that performs inference repeatedly on the same data that is transferred to the GPU once.
%   \item Tahoe does not support multiclass models. We just ran the multiclass models (\op{covtype} and \op{letters})
%   as regression models for the comparison. Tahoe also gives wrong results (as reported by its own tests) for 
%   \op{letters} and \op{year}. In these cases, we pick the time of the fastest variant that gives the correct results.
%   \item Compared the kernel time and total time speedup of \Treebeard{} vs RAPIDS on the RTX 4060 and T400.
%   \item Compared the total time speedup of \Treebeard{} vs XGBoost on the RTX 4060.
%   \item The schedule used was the one picked by the auto-tuner.
%   \item \Treebeard{} outperforms RAPIDS at all batch sizes as shown in Figure \ref{Fig:TBvsRAPIDSTahoe_4060_Speedup}. 
%   \item \Treebeard{} outperforms Tahoe on all models and batch sizes tested. Individual benchmark speedups range between 1.1$\times$ and 16$\times$.
%   \item \Treebeard{} is faster than XGBoost by more than an order of magnitude. Results are not shown because the speedups don't fit on the same graph.
%   \item Figure \ref{Fig:TBvsRAPIDS_4060_TotalTimeSpeedup} shows that \Treebeard{} offers substantial speedup over RAPIDS even when 
%   data needs to be transferred to the GPU and results need to be transferred back.
%   \item Figure \ref{Fig:TBvsRAPIDSTahoe_T400_Speedup} shows that these speedups are also observed on the T400 thus showing 
%   that \Treebeard{} offers portable performance across different GPUs.
%   \item Figure \ref{Fig:KernelTimeIndividualBenchmarks4060} shows that \Treebeard{} outperforms RAPIDS and Tahoe on 
%   individual benchmarks on the RTX 4060 at small (1024) and large (8192) batch sizes. These batch sizes 
%   require different schedules, but the \Treebeard{} auto-tuning heuristic is able to find them.
%   % \item Figure \ref{Fig:TotalTimeIndividualBenchmarks4060} compares the total time of \Treebeard{} vs RAPIDS on individual benchmarks. 
%   % It shows that even with the overhead of data transfers, \Treebeard{} offers significant speedup. The graph in Figure \ref{Fig:TotalTimeIndividualBenchmarks4060} 
%   % shows the breakup of the total time into kernel time and data transfer time.
% \end{itemize}
% \end{comment}

% \begin{figure*}[ht]
%   \centering
%   \begin{subfigure}[b]{.45\textwidth}
%     \subcaptionbox*{}{\includegraphics[width=\textwidth]{figures/abs_times_bar_graph_1024.png}}
%     \caption{Batch size 1024.}
%   \end{subfigure}
%   \begin{subfigure}[b]{.45\textwidth}
%     \subcaptionbox*{}{\includegraphics[width=\textwidth]{figures/abs_times_bar_graph_8192.png}}
%     \caption{Batch size 8192.}
%   \end{subfigure}
%   \hfill
%   \caption{\label{Fig:TotalTimeIndividualBenchmarks4060}\Treebeard{} vs RAPIDS total time comparison on NVIDIA RTX 4060. Numbers on the bars are the times 
%   per sample in $\mu$s for \Treebeard{} and RAPIDS. Times for each benchmark are normalized w.r.t the RAPIDS time for that benchmark.}
% \end{figure*}

% \begin{figure}[htb]
%   \centering
%   \includegraphics[width=0.75\linewidth]{figures/TBvsXGB_TotalTime.png}
%   \caption{\Treebeard{} vs XGBoost Speedup on RTX 4060.}
%   \label{Fig:TBvsXGBoost_Speedup}
% \end{figure}

@@

% \subsubsection*{Exploration Time}
% Finally, we measure the improvement in exploration time that the heuristic provides 
% compared to exhaustive exploration. Figure \ref{Fig:HeuristicVsFullExplore_Speedup} shows that the heuristic
% is consistently close to two orders of magnitude faster than exhaustive exploration. 
% The exploration time ranges between $6$ and $167$ seconds for the heuristic with a mean of $28.7$ seconds.
% These results show that our heuristic is able to quickly find schedules that are close to the best schedule.

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/speedup_vs_norm_time_line_graph_4060.png}
  \caption{Speedup of schedules found by the heuristic vs best schedule found through exhaustive search on NVIDIA RTX 4060 and 
  heuristic schedule exploration time normalized w.r.t full schedule exploration time}
  \label{Fig:HeuristicVsFullExplore_Speedup}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_T400_4060_vs_T400_vs_MI2160.png}
  \caption{Geomean speedup of schedule found by exploration heuristic on NVIDIA T400 and AMD MI2160 vs 
  the heuristic schedule on NVIDIA RTX 4060 across batch sizes}
  \label{Fig:AutotuningSpeedupvs4060Sched}
\end{figure}

% \begin{itemize}
%   \item We compare the schedule found by the schedule exploration heuristic on the RTX 4060 with the best schedule found by
%   extensive exploration. Figure \ref{Fig:HeuristicVsFullExplore_Speedup} shows that the heuristic is able to find schedules that are
%   very close to the best schedule found by exhaustive exploration.
%   \item The speedup of the heuristic schedule vs the best 4060 schedule when run on T400 is shown in Figure \ref{Fig:AutotuningSpeedupvs4060Sched}.
%   Geomean speedup ranges from 1.05$\times$ to 1.2$\times$. 
%   \item Unsurprisingly, there is some variation in the best schedule for a model even across NVIDIA GPUs.
% \end{itemize}

% \begin{itemize}
%   \item \Treebeard{} is able to compile code to AMD GPUs. We run generated code on an AMD MI210 GPU.
%   \item None of the other systems we compare against support running on AMD GPUs. This shows the portability of \Treebeard{}.
%   \item The speedup of the heuristic schedule vs the best 4060 schedule when run on the MI210 is shown in Figure \ref{Fig:AutotuningSpeedupvs4060Sched}.
%   \item We see that the geomean speedup over all benchmarks is 1.5$\times$ at batch size 16k.
%   \item The maximum speedup is 2$\times$ for the \op{letters} benchmark at batch size 16k.
% \end{itemize}

@@

% \begin{itemize}
%   \item The ability of \Treebeard{} to parallelize across both trees and rows has a significant impact on CPU performance.
%   \item We run experiments on the Intel Core i9-11900K processor to evaluate the impact of parallelizing across trees with small batch sizes. 
%   \item At batch size 32, we find that the average speedup over all 8 models is 2.2$\times$ with a max speedup of 5$\times$.
%   \item At batch size 64, we find that the average speedup over all 8 models is 1.1$\times$ with a max speedup of 2$\times$. 
%   However, we find that 2 of the 8 models show slowdowns in this case. Again, this highlights the need for schedule exploration on CPUs.
%   \item For small batch sizes, parallelizing across rows does not work great since there is limited reuse of trees in L1 cache.
%   Also, the amount of work per thread is very small leading to high overheads. 
%   \item Parallelizing across trees is more effective since there is more reuse in L1 cache and the amount of work per thread is higher.  
% \end{itemize}

>>>>

\begin{figure*}[htb]
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/geomean_speedup_4060_kernel_time_total_time.png}
      \caption{\label{Fig:TBvsRAPIDSTahoe_4060_Speedup}Speedup vs batch size}      
    \end{subfigure}
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/speedup_bar_graph_1024.png}
      \caption{\label{Fig:KernelTimeIndividualBenchmarks4060a} Batch size 1024}
    \end{subfigure}
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/speedup_bar_graph_8192.png}
      \caption{\label{Fig:KernelTimeIndividualBenchmarks4060b} Batch size 8192}
    \end{subfigure}
    % \hfill
    \caption{The first graph shows kernel and total time speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
    benchmarks) across batch sizes on NVIDIA RTX 4060. The bar graphs show kernel time speedup of \Treebeard{} over RAPIDS and Tahoe 
    on NVIDIA RTX 4060. Numbers on the bars are inference times per sample in $\mu$s for RAPIDS and Tahoe.}
\end{figure*}

% \begin{figure}[htb]
%   \centering
%   \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_4060_kernel_time_total_time.png}
%   \caption{\Treebeard{} vs RAPIDS and Tahoe kernel time and total time speedup (geomean over real-world 
%   benchmarks) across batch sizes on NVIDIA RTX 4060}
%   \label{Fig:TBvsRAPIDSTahoe_4060_Speedup}
% \end{figure}

@@

% \begin{figure*}[ht]
%   \centering
%   \begin{subfigure}[b]{.45\textwidth}
%     \subcaptionbox*{}{\includegraphics[width=\textwidth]{figures/speedup_bar_graph_1024.png}}
%     \caption{Batch size 1024}
%   \end{subfigure}
%   \begin{subfigure}[b]{.45\textwidth}
%     \subcaptionbox*{}{\includegraphics[width=\textwidth]{figures/speedup_bar_graph_8192.png}}
%     \caption{Batch size 8192}
%   \end{subfigure}
%   \hfill
%   \caption{\label{Fig:KernelTimeIndividualBenchmarks4060}Kernel time speedup of \Treebeard{} vs RAPIDS on NVIDIA RTX 4060. Numbers on the bars are 
%   inference times per sample in $\mu$s for RAPIDS and Tahoe.}
% \end{figure*}

Figures~\ref{Fig:KernelTimeIndividualBenchmarks4060a} and ~\ref{Fig:KernelTimeIndividualBenchmarks4060b} 
show per benchmark results at two different batch sizes. 
\Treebeard{} is able to find better schedules than both RAPIDS and Tahoe on each of the benchmarks. It consistently
outperforms both systems, achieving a speedup of upto $12\times$ and average speedups of over $2\times$.
For about half the benchmarks, the speedup is $2\times$ or more over both baselines at batch size 8192.

@@

\begin{figure}[htb]
  \begin{subfigure}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b512_depth8.png}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b4096_depth6.png}
    \caption{}
  \end{subfigure}
  \caption{\label{fig:randomModels4060}Kernel time speedup of \Treebeard{} over RAPIDS for random models
  of max depth 8 at batch size 512 and max depth 6 at batch size 4096.}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.65\linewidth]{figures/geomean_speedup_T400_kernel_time.png}
  \caption{Speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
  benchmarks) across batch sizes on NVIDIA T400.}
  \label{Fig:TBvsRAPIDSTahoe_T400_Speedup}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.65\linewidth]{figures/speedup_vs_norm_time_line_graph_4060.png}
  \caption{Slowdown of heuristic schedule vs best schedule on NVIDIA RTX 4060 and 
  heuristic schedule exploration time normalized w.r.t full schedule exploration time}
  \label{Fig:HeuristicVsFullExplore_Speedup}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.65\linewidth]{figures/geomean_speedup_T400_4060_vs_T400_vs_MI2160.png}
  \caption{Geomean speedup of heuristic schedule on NVIDIA T400 and AMD MI2160 vs 
  the heuristic schedule on NVIDIA RTX 4060 across batch sizes}
  \label{Fig:AutotuningSpeedupvs4060Sched}
\end{figure}

@@
